---
title: "Demonstration and Testing"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Demonstration and Testing}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r opts, message=FALSE, warning=FALSE, include=FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup, include=FALSE}
library(redcapfiller)
```

Follow these steps to demonstrate the package's capabilities:

- Install the `redcapfiller` package.
    - `install.packages("remotes")` # Run this line if the 'remotes' package isn't installed already.
    - `remotes::install_github("ctsit/redcapfiller")`
- Select a classic REDCap project of your choosing. For a very basic project that exercises all the field types and text validation types, see [REDCapR's validation-types-1 project.xml](https://github.com/OuhscBbmc/REDCapR/blob/main/inst/test-data/projects/validation-types-1/project.xml).
- Make yourself an API token in that project.
- Copy the API token redcap_uri, pid, and other details into a `credentials.csv` that conforms to the specs of [REDCapR::create_credential_local()](https://ouhscbbmc.github.io/REDCapR/reference/retrieve_credential.html).
- Copy [example.env](https://github.com/ctsit/redcapfiller/blob/main/example.env) to your R Project directory and name it `.env`.
- Adjust the value of `path_credential`  in `.env` setting it to the path to your `credentials.csv` created above.
- Adjust the value of `filler_demo_pid` in `.env` to match the project ID of the project you are testing with.
- Open the R project.
- Copy [proof_of_concept.R](https://github.com/ctsit/redcapfiller/blob/main/proof_of_concept.R) into the project directory.
- Open `proof_of_concept.R`.
- Start reading/running the code in `proof_of_concept.R`.
